---
title: "Trust Analysis 2024"
author: "Jordan"
date: "2023-11-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
library(tree)
library(dplyr)
library(rpart.plot)
library(MASS)
library(caret)
library(ztable)
library(GGally)
select <- dplyr::select
```

```{r}
trust_2023_raw_data <- read_csv("trust_2023_raw_data.csv") %>%
  mutate(response = factor(response, order = TRUE, 
                           levels = c("Strongly Disagree", "Disagree", "Nor", "Agree", "Strongly Agree")),
         likertscale = factor(likertscale, ordered = TRUE),
         category = factor(category, levels = c("I", "N", "G", "S"), 
                           labels = c("Infographic", "News", "Government", "Scientific")))
```
## Sources
```{r}
trust_2023_raw_data %>%
  select(category, source, image_new) %>%
  unique() %>%
  group_by(category, source) %>%
  summarise(n = n())
```

```{r}
category_data <- trust_2023_raw_data %>%
  select(c(image_new, category, vistype, starts_with("attr"))) %>%
  unique()
```

```{r}
category_prelim_tree <- rpart(category ~.-image_new , data = category_data, method="class", minsplit = 8)
```

```{r}
rpart.plot(category_prelim_tree, type = 4, clip.right.labs = FALSE, extra=2)
```
## Descriminant analysis
```{r}
#use 80% of dataset as training set and 20% as test set 
train <- category_data %>% dplyr::sample_frac(0.70)
test  <- dplyr::anti_join(category_data, train, by = 'image_new')
train <- train %>% select(-image_new)
text <- test %>% select(-image_new)
lda_category <- lda(category ~. , data = train)
```

```{r}
lda_category
```


```{r}
predictions_LDA = data.frame(predict(lda_category, test))

preds <- cbind(test, predictions_LDA) 


# Confusion Matrix
cf <- caret::confusionMatrix(data=preds$class,
                     reference=test$category)

print(cf)

```

# Believe
## Are there some stimuli that got a wide range or responses?
```{r}
trust_2023_raw_data %>%
  filter(name == "I believe the visualization shows real data.") %>%
  group_by(image_new, response) %>%
  summarise(n= n()) %>%
  arrange(response) %>%
  pivot_wider(names_from = response, values_from = n, values_fill = 0) %>%
  rowwise() %>%
  mutate(total_uses = sum(`Strongly Disagree`, `Disagree`, `Nor`, `Agree`, `Strongly Agree`)) %>%
  filter(total_uses > 1) %>%
  arrange(desc(total_uses))
```

## (balanced sampling, n = 125 per group)
Note: remember to drop session_id, etc. or you'll be waiting foreverrrrrr...
```{r}
believe_data <- trust_2023_raw_data %>%
  filter(name == "I believe the visualization shows real data.") %>%
  group_by(likertscale) %>%
  sample_n(125) %>%
  ungroup() %>%
  #mutate(age_cat = cut(age, breaks = c(-Inf,35,50,Inf), labels = c("Under 35", "36-49", "Over 50"))) %>%
  select(-c(...1, name, session_id, image, subfolder, category, likertscale, time,
            starts_with("title"), starts_with("mem"), question_type, cluster, source))
```

```{r}
believe_prelim_tree <- rpart(response ~.-image_new , data = believe_data, method="class", minsplit = 4)
```

```{r}
rpart.plot(believe_prelim_tree, type = 4, clip.right.labs = FALSE, extra=2)
```
## Next steps

#. Label original believe_data with leaf node each observation falls in (maybe a `join(...)` with `predict(...)`?)
#. `group_by` leaf node
#. Select `unique()` images
#. Make some kind of collage so we can look for visual trends
#. Original images can be found at: https://people.csail.mit.edu/zoya/VisThumbnails/fullsize/

```{r}
believe_pred = predict(believe_prelim_tree, believe_data, type = "class")

table(believe_pred, believe_data$response)
```
## Predicted vs. true
```{r}
believe_data_with_pred <- cbind(believe_data, pred = believe_pred) %>%
  mutate(pred = factor(pred, order = TRUE, 
                           levels = c("Strongly Disagree", "Disagree", "Nor", "Agree", "Strongly Agree")))
```  

## Are there some stimuli that got a wide range or responses?
```{r}
believe_data_with_pred %>%
  group_by(image_new, response) %>%
  summarise(n= n()) %>%
  arrange(response) %>%
  pivot_wider(names_from = response, values_from = n, values_fill = 0) %>%
  rowwise() %>%
  mutate(total_uses = sum(`Strongly Disagree`, `Disagree`, `Nor`, `Agree`, `Strongly Agree`)) %>%
  filter(total_uses > 1) %>%
  arrange(desc(total_uses))
```

## Images with largest errors
```{r}
believe_data_with_pred %>%
  group_by(image_new, response) %>%
  summarise(n= n(),
            pred = pred) %>%
  mutate(error = as.numeric(response) - as.numeric(pred)) %>%
  filter(abs(error) > 2) %>%
  arrange(image_new, desc(n))
```


# balanced sampling for strongly agree and disagree:

## Credibility:


```{r}
strongly_believe_data <- trust_2023_raw_data %>%
  filter(name == "I believe the visualization shows real data." & (response == "Strongly Agree" | response == "Strongly Disagree")) %>%
  group_by(likertscale) %>%
  sample_n(125) %>%
  ungroup() %>%
  select(-c(...1, name, session_id, image, subfolder, category, likertscale, time,
            starts_with("title"), starts_with("mem"), question_type, cluster, source))
```


```{r}
strong_belief_prelim_tree <- rpart(response ~.-image_new , data = strongly_believe_data, method="class")
```

```{r}
rpart.plot(strong_belief_prelim_tree, type = 4, clip.right.labs = FALSE, extra=2)
```

##Clarity:

```{r}
strongly_clear_data <- trust_2023_raw_data %>%
  filter(name == "I understand what this visualization is trying to tell me." & (response == "Strongly Agree" | response == "Strongly Disagree")) %>%
  group_by(likertscale) %>%
  sample_n(125) %>%
  ungroup() %>%
  select(-c(...1, name, session_id, image, subfolder, category, likertscale, time,
            starts_with("title"), starts_with("mem"), question_type, cluster, source))
```


```{r}
strong_clarity_prelim_tree <- rpart(response ~.-image_new , data = strongly_clear_data, method="class")
```

```{r}
rpart.plot(strong_clarity_prelim_tree, type = 4, clip.right.labs = FALSE, extra=2)
```

##Reliability:

```{r}
strongly_reliable_data <- trust_2023_raw_data %>%
  filter(name == "I would rely on the facts in this Visualization." & (response == "Strongly Agree" | response == "Strongly Disagree")) %>%
  group_by(likertscale) %>%
  sample_n(125) %>%
  ungroup() %>%
  select(-c(...1, name, session_id, image, subfolder, category, likertscale, time,
            starts_with("title"), starts_with("mem"), question_type, cluster, source)) 
ggpairs(strongly_reliable_data)
```


```{r}
strong_reliability_prelim_tree <- rpart(response ~.-image_new , data = strongly_reliable_data, method="class")
```

```{r}
rpart.plot(strong_reliability_prelim_tree, type = 4, clip.right.labs = FALSE, extra=2)
```

##Familiarity

```{r}
strongly_familiar_data <- trust_2023_raw_data %>%
  filter(name == "I am familiar with the topic or data this visualization presents." & (response == "Strongly Agree" | response == "Strongly Disagree")) %>%
  group_by(likertscale) %>%
  sample_n(125) %>%
  ungroup() %>%
  select(-c(...1, name, session_id, image, subfolder, category, likertscale, time,
            starts_with("title"), starts_with("mem"), question_type, cluster, source))
```


```{r}
strong_familiar_prelim_tree <- rpart(response ~.-image_new , data = strongly_familiar_data, method="class")
```

```{r}
rpart.plot(strong_familiar_prelim_tree, type = 4, clip.right.labs = FALSE, extra=2)
```

##Confidence:


```{r}
strong_confidence_data <- trust_2023_raw_data %>%
  filter(name == "I believe the visualization shows real data." & (response == "Strongly Agree" | response == "Strongly Disagree")) %>%
  group_by(likertscale) %>%
  sample_n(125) %>%
  ungroup() %>%
  select(-c(...1, name, session_id, image, subfolder, category, likertscale, time,
            starts_with("title"), starts_with("mem"), question_type, cluster, source))
```


```{r}
strong_confidence_prelim_tree <- rpart(response ~.-image_new , data = strong_confidence_data, method="class")
```

```{r}
rpart.plot(strong_confidence_prelim_tree, type = 4, clip.right.labs = FALSE, extra=2)
```

